\input{Header.tex}

\usepackage[procnames]{listings}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%
%		Caratula		%
%%%%%%%%%%%%%%%%%%%%%%%%%

\input{Caratula.tex}

%%%%%%%%%%%%%%%%%%%%%
%		Indice		%
%%%%%%%%%%%%%%%%%%%%%

%\tableofcontents
%\newpage

%%%%%%%%%%%%%%%%%%%%%
%		Informe		%
%%%%%%%%%%%%%%%%%%%%%

\title{Illumination Robust Object Tracking Using Optical Flow, Correlation Filtering and Color-Distribution-Based Image Masking}
\author{Mechoulam Alan, Lambertucci Guido, Rodriguez Turco Martín, Londero Bonaparte Tomás\\
\small{Instituto Tecnológico de Buenos Aires, Argentina}}

\twocolumn[
  \begin{@twocolumnfalse}
    \maketitle
    \begin{abstract}
		\input{secciones/abstracto.tex}
	\end{abstract}
  \end{@twocolumnfalse}
  ]

%\begin{figure*}



%\maketitle

%\begin{abstract}
%\input{secciones/abstracto.tex}
%\end{abstract}

%\end{figure*}


\section{Introducción}
\input{secciones/introduccion.tex}
	
\section{Investigación}
\input{secciones/investigacion.tex}

\section{Aportes y Desarrollo}
\input{secciones/aportes.tex}

%\section{Trabajo en futuro}
%\input{secciones/mejoras.tex}

\section{Conclusiones}
\input{secciones/conclusion.tex}

\begin{thebibliography}{9}

\bibitem{ref:intro1}
R. C. Gonzalez, R. E. Woods y S. L. Eddins. \textit{Digital Image Processing Using MATLAB}. Prentice Hall, 2da ed, 2002.%, pp. 2-3.

\bibitem{ref:digit1}
R. C. Gonzalez, R. E. Woods y S. L. Eddins. \textit{Digital Image Processing Using MATLAB}. Prentice Hall, 2da ed, 2002, pp. 52-54.

\bibitem{ref:optic-flow}
D. H. Warren y Edward R. Strelow. \textit{Electronic Spatial Sensing for the Blind: Contributions from Perception}. Springer Netherlands, 1er ed, 1985. pp. 414.

\bibitem{ref:lucas-kanade}
B. D. Lucas y T. Kanade. \textit{An iterative image registration technique with an application to stereo vision}. De Proceedings of Imaging Understanding Workshop, pp. 121-130.

\bibitem{ref:shi-tomasi}
J. Shi y C. Tomasi. \textit{Good Features to Track}. 9th IEEE Conference on Computer Vision and Pattern Recognition, June 1994, Springer, pp. 593–600.

\bibitem{ref:lucas-kanade2}
W.S.P. Fernando, L. Udawatta , P. Pathirana. \textit{Identification of Moving Obstacles with Pyramidal
Lucas Kanade Optical Flow and k means
Clustering}. Faculty of Engineering, University of Moratuwa, Sri Lanka.

\bibitem{ref:kalman1}
G. Terejanu, "Discrete Kalman Filter Tutorial", Cse.sc.edu, 2020. [Online]. Available: https://cse.sc.edu/~terejanu/files/tutorialKF.pdf. [Accessed: 15- Jun- 2020].

\bibitem{ref:kalman2}
G. Welch and G. Bishop, An Introduction to the Kalman Filter. University of North Carolina at Chapel Hill: Department of Computer Science, 2006.

\bibitem{ref:shi-tomasi}
J. Shi y C. Tomasi. \textit{Good Features to Track}. 9th IEEE Conference on Computer Vision and Pattern Recognition, June 1994, Springer, pp. 593–600.
 \bibitem{ref:Corr}
 G. Turin, "An introduction to matched filters," in IRE Transactions on Information Theory, vol. 6, no. 3, pp. 311-329, June 1960, doi: 10.1109/TIT.1960.1057571.


\end{thebibliography}

\end{document}